We Are All Trying to Describe Something And We Don't Have the Words

### 2023-04-19 outputs/paper/paper.qmd
more edits

I spoke to Caleb Gamman, a Youtuber and Antonoff-production-style hater who had a tweet go viral around the time of Taylor Swift's *Midnights* release, in which he predicts whether or not a song was produced by Antonoff within seconds. A real-life logistic regression, if you will. Using an actual logistic regression model, I was able to determine that Spotify's `danceability` feature was the most important in predicting whether or not a song had any Antonoff involvement. During an interview with Glen McDonald, an engineer at Spotify, I learned that the `valence` and `danceability` variables were created by hiring college interns to tag whether or not songs were positive or danceable. In the discussion section, I listen to the songs with the highest danceability scores, and make an argument that this `danceability` feature, which has so much uncertainty cooked into it, is really capturing visceral-ness. We can capture something about Antonoff's music with these variables, and it might just be that subjective "ick" that many people feel and others enjoy that we're all just trying to describe.

>>>>

I spoke to Caleb Gamman, a Youtuber and Antonoff-production-style hater who had a tweet go viral around the time of Taylor Swift's *Midnights* release, in which he predicts whether or not a song was produced by Antonoff within seconds. A real-life logistic regression, if you will. Using an actual logistic regression model, I was able to determine that Spotify's `danceability` feature was the most important in predicting whether or not a song had any Antonoff involvement. During an interview with Glen McDonald, an engineer at Spotify, I learned that the `valence` and `danceability` variables were created by hiring college interns to tag whether or not songs were positive or danceable. In the discussion section, I listen to the songs with the highest danceability scores, and make an argument that this `danceability` feature, which has so much uncertainty cooked into it, is really capturing something like visceral-ness. We can capture something about Antonoff's music with these variables, and it might just be that subjective "ick" that many people feel and others enjoy and that we're all just trying to describe.
